---
title: "High Dimensional Selection with Interactions Algorithm on Feature Selection for Time-to-Event Outcome"
#subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Lin Yu"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    self_contained: true
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)

```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```


```{r xaringanExtra-search, echo=FALSE}
xaringanExtra::use_search(show_icon = TRUE)
xaringanExtra::style_search(match_background = "skyblue")
xaringanExtra::use_clipboard()
xaringanExtra::use_scribble()
xaringanExtra::use_tile_view() ## press O 
xaringanExtra::use_progress_bar(color = "#3C989E", location = "bottom")
xaringanExtra::use_extra_styles(
  hover_code_line = TRUE,         
  mute_unhighlighted_code = TRUE  
)
```


# Background

This .purple[word] is purple.

---
class: center, middle 
```{r echo=FALSE, fig.height=6.5, fig.width=8, dpi=300}
## this is a test
```

---
## Notation
Original dataset:
- Sample size (n): total number of observations
- feature dimension (p): total number of features

Feature selection
1. prepare bootstrap samples
- each bootstrapped data set has
  - n observations (use bootstrap with replacement)
  - q features (hyperparameter bootstrap without replacement)
  
2. prepare interaction terms

3. apply lasso, adaptive lasso, regression to get the estimates of all beta coefficients

4. compute averaged value of beta estimate, and min(R^2) of each feature

5. select features using two criteria:
  - quantiles of B estimates should not include zero (significant) (hyperparameter)
  - 
  


  
  


